### 2011-10-09 doc/theses/vitasek/chapter-4-2-experiments-results.tex
Thesis: in progress

>>>>

We will now present the experiments we performed along with their results and conclusions. Each experiment will be introduced with a table summarizing the most important parameters of the experiment, such as data used, number of iterations and CH pool size, $\alpha$ and $\beta$ parameters and the actual heuristics used.
